\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{RGB}{0,0,139}
\definecolor{graytext}{RGB}{80,80,80}

% Custom section formatting
\titleformat{\section}{\Large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{14pt}{7pt}

% Custom itemize formatting
\setlist[itemize]{leftmargin=1.5em, nosep, topsep=3pt, itemsep=3pt}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

\begin{document}

%----------------------------------------------------------------------------------------
%	HEADER
%----------------------------------------------------------------------------------------
\begin{center}
    {\Huge \textbf{Gopi Krishna Tummala}} \\ [6pt]
    \large
    \faMapMarker* Fremont, CA \quad | \quad
    \faPhone* +1-614-620-7960 \quad | \quad
    \faEnvelope* \href{mailto:tummalag.cseosu@gmail.com}{tummalag.cseosu@gmail.com} \\ [4pt]
    \small
    \faLinkedin \href{https://www.linkedin.com/in/gopi-krishna-tummala-00294415/}{ linkedin.com/in/gopi-krishna-tummala} \quad | \quad
    \faGlobe \href{https://gopikrishnatummala.com/}{ gopikrishnatummala.com} \quad | \quad
    \faGraduationCap \href{https://scholar.google.com/citations?user=SaKqqO8AAAAJ&hl=en}{ Google Scholar} \\ [4pt]
    \textbf{Visa Status:} Green Card
\end{center}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
Machine Learning Engineer with \textbf{12+ years of experience} designing and deploying scalable ML systems for \textbf{Generative AI} and \textbf{Autonomous Driving} (L3-L5). Expert in developing \textbf{AV prediction models} and building production training infrastructure, custom GPU kernels, and multi-modal data pipelines. Proven track record of bridging research and production, with a Ph.D. in Computer Science, 10+ patents, and award-winning publications. Currently architecting data infrastructure for Adobe Firefly.

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{itemize}
    \item \textbf{Languages:} Python (Expert), C++, CUDA, SQL, Bash, TypeScript, Java, HTML/CSS.
    \item \textbf{ML \& GenAI:} PyTorch, TensorFlow, JAX, Transformers, Diffusion Models (DiT/VAE), Vision-Language Models (VLMs), RAG, LangChain, FlashAttention, vLLM.
    \item \textbf{Infrastructure:} Distributed Training (FSDP, DeepSpeed), AWS (S3, DynamoDB, EC2), Docker, Kubernetes, Ray, Apache Arrow/Parquet.
    \item \textbf{Domain Expertise:} Autonomous Vehicles (Prediction/Planning), Computer Vision, Sensor Fusion, Camera Calibration, MLOps.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Professional Experience}

\textbf{Adobe} \hfill San Jose, CA \\
\textit{Senior Machine Learning Engineer} \hfill Sep 2024 -- Present
\begin{itemize}
    \item \textbf{GenAI Data Marketplace:} Architecting a high-performance Data Marketplace (internal Hugging Face) to support \textbf{Adobe Firefly}, serving distinct data needs across research and product teams.
    \item \textbf{Production Dataloader:} Developed/Maintained a high-throughput dataloader for production training, handling \textbf{$>$1M calls/month} with optimized data streaming and caching.
    \item \textbf{Scalable Storage:} Managed a global training feature store on a \textbf{DynamoDB cluster (~20B items)}, ensuring high availability and low-latency access for distributed training jobs.
    \item \textbf{MLOps \& Profiling:} Engineered runtime profiling suites and CI/CD automation for high-throughput dataloaders and inference systems, optimizing resource utilization and accelerating deployment velocity.
\end{itemize}

\textbf{Zoox} \hfill Foster City, CA \\
\textit{Software Engineer - Prediction} \hfill Apr 2022 -- Aug 2024
\begin{itemize}
    \item Built prediction visualization plugin for Argus (ROS/RViz-like viewer) using TypeScript/React, Python, C++ to debug probabilistic multi-trajectory outputs across the AV stack.
    \item Modernized vehicular prediction: designed stable ground-truth labeling algorithm using agent direction + road target/waypoint orientation (TNT-inspired target-driven approach); replaced flickery closest-distance heuristic → delivered 2--3 production releases with major gains in intent/target and trajectory accuracy.
    \item Overhauled VRU (pedestrian/cyclist/motorcycle) prediction: migrated legacy CNN/top-down + MLP to transformer-based multi-intent/trajectory architecture; solved intent generation for off-road/ambiguous agents → outperformed mature baseline; owned PyTorch → ONNX → custom C++ runtime deployment.
    \item \textbf{Led} TensorFlow → PyTorch Lightning migration: built config-driven module registry (YAML/Proto) for MLPs, CNNs, LSTMs, GNNs, Transformers, UNet backbones; integrated wandb/CometML; achieved near-parity for key models.
    \item \textbf{Led} framework infrastructure: scalable PyTorch dataloaders (TF Records → NPZ) and large-scale evaluation framework (~40,000 scenarios/batch); authored novel intent/trajectory metrics surfaced via Streamlit dashboard.
\end{itemize}

\textbf{Qualcomm Research} \hfill San Diego, CA \\
\textit{Systems Engineer} \hfill Jan 2019 -- Feb 2022
\begin{itemize}
    \item Replaced rule-based prediction with XGBoost multi-class classifier (lane keep, lane changes); built data pipeline parsing/annotating ROS bags → trained model beating baseline → hand-wrote C++ inference engine for Snapdragon Ride platform (zero external dependencies).
    \item Led GRIP++ (RNN+CNN-based) trajectory prediction implementation: developed custom rasterization pipeline to convert raw ROS logs into training-ready visual renders; achieved state-of-the-art results by 2021.
    \item Built automated Python pipelines for ROS bag analysis: extracted prediction metrics, generated weekly HTML reports for stack validation; integrated with AVS internal simulator for closed-loop testing of perception/planning modules.
    \item Filed 2--3 patents on Vehicle-to-Vehicle (V2V) communication and prediction corner cases for autonomous driving.
\end{itemize}

\textbf{Standard Chartered Scope International} \hfill Chennai, India \\
\textit{Software Analyst} \hfill Jun 2012 -- Jul 2013
\begin{itemize}
    \item Developed financial software systems and data analysis tools for banking operations.
\end{itemize}

%----------------------------------------------------------------------------------------
%	RESEARCH INTERNSHIPS
%----------------------------------------------------------------------------------------
\section{Research Internships}

\textbf{Qualcomm Research} \hfill San Diego, CA \\
\textit{Systems Integration \& Test Intern} \hfill Summer 2018
\begin{itemize}
    \item Developed prediction metrics framework: analyzed ROS bags using Python APIs, extracted performance metrics from rule-based prediction system, generated automated HTML reports for weekly reviews.
\end{itemize}

\textbf{Microsoft Research} \hfill Bangalore, India \\
\textit{Research Intern} \hfill Summer 2016
\begin{itemize}
    \item \textbf{Project AutoCalib:} Designed software for automatic traffic camera calibration. Achieved speed estimation errors of $<10\%$ without manual intervention.
    \item Published results in \textit{ACM BuildSys 2017} (Won Best Paper Award).
\end{itemize}

\textbf{Tata Elxsi} \hfill Chennai, India \\
\textit{Project Intern} \hfill Summer 2011

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{The Ohio State University} \hfill Columbus, OH \\
\textit{Ph.D. in Computer Science \& Engineering} \hfill 2013 -- 2018 \\
\textit{M.S. in Computer Science \& Engineering} \hfill 2013 -- 2017

\textbf{IIT Madras} \hfill Chennai, India \\
\textit{B.Tech in Electrical Engineering (Minor in Mathematics)} \hfill 2008 -- 2012

%----------------------------------------------------------------------------------------
%	SELECTED PUBLICATIONS
%----------------------------------------------------------------------------------------
\section{Selected Publications}
\begin{itemize}
    \item \textbf{AutoCalib: Automatic calibration of traffic cameras at scale.} \\
    \textit{ACM Transactions on Sensor Networking (TOSN) 2018} \& \textit{ACM BuildSys 2017}. \\
    \textbf{Awards:} Best Paper Award \& Best Demo Award.
    \item \textbf{SmartDashCam: Automatic Live Calibration for DashCams.} \\
    \textit{ACM IPSN 2019}.
    \item \textbf{RoadView: Live View of On-Road Vehicular Information.} \\
    \textit{IEEE SECON 2017}.
    \item \textbf{CaneScanner: Obstacle Detection for People with Visual Disabilities.} \\
    \textit{IEEE INFOCOM 2018}.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PATENTS (SELECTED)
%----------------------------------------------------------------------------------------
\section{Patents}
\textit{10+ patents granted/pending in AV prediction, behavior trees, and calibration.}
\begin{itemize}
    \item \textbf{US Patent 10,580,164:} Automatic Camera Calibration (Microsoft).
    \item \textbf{US Patent 10,032,370:} Methods for enabling Mobile communication device based Secure Interaction (Honda).
    \item \textbf{US Patent 12,542,054:} Managing vehicle behavior based on predicted behavior of other vehicles (Qualcomm).
    \item \textbf{US Patent App 17/352,886:} Tree based behavior predictor (Qualcomm).
\end{itemize}

%----------------------------------------------------------------------------------------
%	HONORS & SERVICE
%----------------------------------------------------------------------------------------
\section{Honors \& Service}
\begin{itemize}
    \item \textbf{Awards:} Best Paper (ACM BuildSys 2017), Best Demo (IEEE MiSeNet 2018), NSF Travel Awards (2017, 2018).
    \item \textbf{Scholastic:} All India Rank 274 (Top 0.1\%) in IIT-JEE; Top 1\% in National Physics/Math Olympiads.
    \item \textbf{Service:} Associate Editor for \textit{IEEE RA-L}; Reviewer for \textit{ACM TECS}, \textit{IEEE TMC}, \textit{ToSN}.
    \item \textbf{Technical Blog:} Author of \href{https://gopikrishnatummala.com/}{gopikrishnatummala.com}, publishing in-depth technical deep dives on generative AI and model scaling, advanced MLOps and production-grade infrastructure, autonomous systems engineering, and agentic AI design and deployment.
\end{itemize}

\end{document}