\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fontawesome5}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{RGB}{0,0,139}
\definecolor{graytext}{RGB}{80,80,80}

% Custom section formatting
\titleformat{\section}{\Large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{14pt}{7pt}

% Custom itemize formatting
\setlist[itemize]{leftmargin=1.5em, nosep, topsep=3pt, itemsep=3pt}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
}

\begin{document}

%----------------------------------------------------------------------------------------
%	HEADER
%----------------------------------------------------------------------------------------
\begin{center}
    {\Huge \textbf{Gopi Krishna Tummala}} \\ [6pt]
    \large
    \faMapMarker* Fremont, CA \quad | \quad
    \faPhone* +1-614-620-7960 \quad | \quad
    \faEnvelope \href{mailto:tummalag.cseosu@gmail.com}{tummalag.cseosu@gmail.com} \\ [4pt]
    \small
    \faLinkedin \href{https://www.linkedin.com/in/gopi-krishna-tummala-00294415/}{ linkedin.com/in/gopi-krishna-tummala} \quad | \quad
    \faGlobe \href{https://gopikrishnatummala.com/}{ gopikrishnatummala.com} \quad | \quad
    \faGraduationCap \href{https://scholar.google.com/citations?user=SaKqqO8AAAAJ&hl=en}{ Google Scholar} \\ [4pt]
    \textbf{Visa Status:} Green Card
\end{center}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Professional Summary}
Technically hands-on Machine Learning Engineering Leader with \textbf{12+ years of experience} architecting scalable ML infrastructure for \textbf{Generative AI} and \textbf{Autonomous Driving} (L3-L5). Proven track record of transitioning complex research into robust production systems while leading, mentoring, and scaling engineering teams. Deep expertise in distributed training infrastructure, high-throughput data pipelines, and MLOps. Passionate about driving technical vision, fostering engineering excellence, and empowering teams to deliver high-impact AI platforms.

%----------------------------------------------------------------------------------------
%	CORE COMPETENCIES & TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Core Competencies \& Technical Skills}
\begin{itemize}
    \item \textbf{Engineering Leadership:} Technical Strategy \& Roadmap, Cross-Functional Team Leadership, Mentorship, Agile Project Execution, Research-to-Production Lifecycle.
    \item \textbf{ML Infrastructure:} Distributed Training (FSDP, DeepSpeed), AWS (S3, DynamoDB, EC2), Docker, Kubernetes, Ray, Apache Arrow/Parquet.
    \item \textbf{Machine Learning \& GenAI:} PyTorch, JAX, Transformers, Diffusion Models (DiT/VAE), Vision-Language Models (VLMs), vLLM.
    \item \textbf{Languages:} Python (Expert), C++, CUDA, SQL, Bash, TypeScript, Java.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Professional Experience}

\textbf{Adobe} \hfill San Jose, CA \\
\textit{Senior Machine Learning Engineer \& Tech Lead} \hfill Sep 2024 -- Present
\begin{itemize}
    \item \textbf{Team Leadership \& Architecture:} Lead a team of 3 engineers in architecting a high-performance Data Marketplace (internal Hugging Face equivalent) to centralize and scale data access for the \textbf{Adobe Firefly} GenAI organization.
    \item \textbf{Infrastructure Scaling:} Directed the design and deployment of a global training feature store utilizing a distributed \textbf{DynamoDB cluster (~20B items)}, ensuring ultra-low latency and high availability for distributed training workloads.
    \item \textbf{Performance Optimization:} Spearheaded the development of a high-throughput production dataloader handling \textbf{$>$1M calls/month}. Engineered advanced data streaming and caching mechanisms that significantly reduced training bottlenecks.
    \item \textbf{MLOps Excellence:} Established CI/CD automation and runtime profiling suites for inference systems, driving engineering best practices that accelerated deployment velocity and optimized compute resource utilization.
\end{itemize}

\textbf{Zoox} \hfill Foster City, CA \\
\textit{Software Engineer (Prediction) \& Tech Lead} \hfill Apr 2022 -- Aug 2024
\begin{itemize}
    \item \textbf{Modeling:} Delivered vehicular and VRU (pedestrian/cyclist) prediction improvements; transitioned legacy CNN/MLP architectures to transformer-based models, outperforming mature baselines.
    \item \textbf{Framework Migration (Led):} Spearheaded the organization-wide migration from TensorFlow to PyTorch Lightning. Architected config-driven module registry and integrated experiment tracking (wandb/CometML), achieving near-parity for mission-critical models.
    \item \textbf{Data \& Evaluation Infra (Led):} Directed development of scalable PyTorch dataloaders (TF Records → NPZ) and large-scale evaluation framework (\textbf{~40,000 scenarios per batch}).
    \item \textbf{Cross-Functional Tooling:} Championed the development of a prediction visualization plugin for the Argus viewer (TypeScript/React, Python, C++), enabling cross-stack debugging of probabilistic trajectories.
\end{itemize}

\textbf{Qualcomm Research} \hfill San Diego, CA \\
\textit{Systems Engineer} \hfill Jan 2019 -- Feb 2022
\begin{itemize}
    \item \textbf{Mentorship \& Execution:} Managed and mentored 1 L4 engineer. Led the end-to-end development of a rule-based prediction replacement using an XGBoost multi-class classifier, managing the data pipeline, training, and deployment phases.
    \item \textbf{Production Inference:} Architected and hand-wrote a zero-dependency C++ inference engine for the Snapdragon Ride platform, successfully bridging Python-based research with constrained on-device environments.
    \item \textbf{System Integration:} Built automated validation pipelines for ROS bag analysis, extracting key metrics and generating reports that drove the weekly perception/planning integration cycle.
\end{itemize}

\textbf{Standard Chartered Scope International} \hfill Chennai, India \\
\textit{Software Analyst} \hfill Jun 2012 -- Jul 2013
\begin{itemize}
    \item Developed financial software systems and data analysis tools for global banking operations.
\end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\textbf{The Ohio State University} \hfill Columbus, OH \\
\textit{Ph.D. in Computer Science \& Engineering} \hfill 2013 -- 2018 \\
\textit{M.S. in Computer Science \& Engineering} \hfill 2013 -- 2017

\textbf{IIT Madras} \hfill Chennai, India \\
\textit{B.Tech in Electrical Engineering (Minor in Mathematics)} \hfill 2008 -- 2012

%----------------------------------------------------------------------------------------
%	SELECTED PUBLICATIONS & THOUGHT LEADERSHIP
%----------------------------------------------------------------------------------------
\section{Selected Publications \& Thought Leadership}
\begin{itemize}
    \item \textbf{Technical Blog:} Author of \href{https://gopikrishnatummala.com/}{gopikrishnatummala.com}, publishing in-depth technical deep dives on generative AI and model scaling, advanced MLOps, production-grade infrastructure, and autonomous systems.
    \item \textbf{AutoCalib: Automatic calibration of traffic cameras at scale.} \\
    \textit{ACM Transactions on Sensor Networking (TOSN) 2018} \& \textit{ACM BuildSys 2017}. \textbf{Awards:} Best Paper \& Best Demo.
    \item \textbf{SmartDashCam: Automatic Live Calibration for DashCams.} \textit{ACM IPSN 2019}.
    \item \textbf{Service \& Honors:} Associate Editor for \textit{IEEE RA-L}; Reviewer for \textit{ACM TECS}, \textit{IEEE TMC}; All India Rank 274 (Top 0.1\%) in IIT-JEE; Best Paper (IEEE INFOCOM 2018 MiSeNet).
\end{itemize}

%----------------------------------------------------------------------------------------
%	PATENTS
%----------------------------------------------------------------------------------------
\section{Patents}
\textit{10+ patents granted/pending spanning ML infrastructure, AV prediction, and system calibration.}
\begin{itemize}
    \item \textbf{US Patent 10,580,164:} Automatic Camera Calibration (Microsoft).
    \item \textbf{US Patent 10,032,370:} Methods for enabling Mobile communication device based Secure Interaction (Honda).
    \item \textbf{US Patent 12,542,054:} Managing vehicle behavior based on predicted behavior of other vehicles (Qualcomm).
    \item \textbf{US Patent App 17/352,886:} Tree based behavior predictor (Qualcomm).
\end{itemize}

\end{document}
